Correcting K-correction: dark energy is based on a math error from 1930

### 2025-02-04 paper/dark_energy_corrections.tex

\begin{quote}
  An appropriate K-correction quantifies the difference between the supernova
  light that falls into a standard passband (e.g., $B$) at $z_0$ and that which
  falls into the filters we employ to observe a redshifted SN Ia.
\end{quote}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{k_equation_flow.pdf}
  \caption{The value $K'_{xy}$ is equal to the number of photons we want to
  report in the target filter divided by the number of photons we measure in
  the observation filter. Deriving this value starts with $F(\lambda)$, the
  spectral energy density, which we then convert to $F'(\lambda)$, the photon
  density for the rest frame. Starting at the top right corner of the figure we
  show three steps used to compute $R'(\lambda)$, the photon density in the
  observation frame. We first stretch the photon density, but this step
  inflates counts. In the second step, we correct for the inflated counts by
  multiplying by $1/(1+z)$; at this point, the total count equals the total
  count of $F'(\lambda)$. Finally, in the third step we finish calculating the
  observation frame photon density $R'(\lambda)$ by accounting for time
  dilation, which also reduces photon counts by a factor of $1/(1+z)$. We can
  compute the expected ratio of photons by totalling the area under the curves
  in the bottom two panels. Dark energy occurs when we omit the step that
  corrects for time dilation.
  }
  \label{fig:k-example}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{velocity_vs_distance.pdf}
  \caption{The relationship between expansion velocity and light travel
  distance. The slope of this graph demonstrates the Hubble constant. The data
  for these SN Ia observations comes from the Dark Energy Survey
  \citep{vincenzi2024}, but the magnitudes are corrected to account for time
  dilation by adding $-2.5 \text{log}(1 + z)$.
  }
\label{fig:expansion}
\end{figure}

@@

The value estimated here, $H_0 = 65.94 \pm 1.3$, is highly suspicious
because of the flipped zero-point corrections, but it is consistent with
estimates of $H_0$ that are based on the CMB. \citet{planck2020} published the
CMB value of $H_0 = 67.27 \pm 0.6$, and the one sigma error bars overlap. It
is interesting to note that restricting the Dark Energy Survey observations of
SN Ia \citep{vincenzi2024} to only those with $z < 0.1$, which presumably is a
small enough redshift that most of the observations will have been made with
the same filter, gives the estimate $H_0 = 67.8 \pm 1.9$.

>>>>

\begin{quote}
  An appropriate K-correction quantifies the \emph{difference} between the supernova
  light that falls into a standard passband (e.g., $B$) at ${z = 0}$ and that
  which falls into the filters we employ to observe a redshifted SN Ia.
\end{quote}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{k_equation_flow.pdf}
  \caption{The value $\mathcal{F}_x / \mathcal{F}_y$ is equal to the number of
  photons we want to report in the target filter divided by the number of
  photons we measure in the observation filter. Deriving this value starts with
  $F(\lambda)$, the spectral energy density, which we then convert to
  $F'(\lambda)$, the photon density for the rest frame. Starting at the top
  right corner of the figure we show three steps used to compute $R'(\lambda)$,
  the photon density in the observation frame. We first stretch the photon
  density, but this step inflates counts. In the second step, we correct for
  the inflated counts by multiplying by $1/(1+z)$; at this point, the total
  count equals the total count of $F'(\lambda)$. Finally, in the third step we
  finish calculating the observation frame photon density $R'(\lambda)$ by
  accounting for time dilation, which also reduces photon counts by a factor of
  $1/(1+z)$. We can compute the expected ratio of photons by totalling the area
  under the curves in the bottom two panels. Dark energy occurs when we omit
  the step that corrects for time dilation.
  }
  \label{fig:k-example}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{velocity_vs_distance.pdf}
  \caption{The relationship between expansion velocity and light travel
  distance. The slope of this graph demonstrates the Hubble constant. The data
  for these SN Ia observations comes from the Dark Energy Survey
  \citep{vincenzi2024}, but the magnitudes are corrected to account for time
  dilation by adding ${-2.5 \text{log}(1 + z)}$.
  }
\label{fig:expansion}
\end{figure}

@@

The value estimated here, $H_0 = 65.94 \pm 1.3$, is highly suspicious
because of the flipped zero-point corrections, but it is consistent with
estimates of $H_0$ that are based on the CMB. \citet{planck2020} published the
CMB value of $H_0 = 67.27 \pm 0.6$, and the one sigma error bars overlap.
